The Host Galaxies of Rapidly Evolving Transients in the Dark Energy Survey

### 2020-03-18 RET_Hosts_IR.tex

\section{Estimating host galaxy properties}
\label{sec:measure}
\subsection{SED fitting \label{subsec:sedfit}}
To estimate the physical properties of the DES RET host galaxies, we generate synthetic photometry in the DES $griz$ bands by combining the individual SEDs of simple stellar population models. We simulate a suite of synthetic galaxy star-formation histories from which we synthesise model SEDs using stellar population models from \citet{Bruzual2003}  and a \citet{Chabrier2003} initial mass function (IMF).  The suite of models is drawn from the same distribution of parameters as used in \citet{Kauffmann2003} and similar papers \citep[e.g.][]{Gallazzi2005,Gallazzi2009} and closely follows the method of \citet{Childress2013}. From the synthetic SEDs we derive model magnitudes in the DES $griz$ bands and compare them to the observed magnitudes. For each set of model and observed magnitudes we calculate a $\chi^2$ value, and from these calculate a PDF for  key model parameters (mass-to-light ratio $M/L$ and specific star-formation rate sSFR). To estimate uncertainties, we take the values at the 16th and 84th percentiles of the resulting PDF to be our $1\sigma$ lower and upper bounds. The results are presented in Table \ref{tab:derived}.

\subsection{Spectral line fitting \label{subsec:linefit}}

To estimate parameters from the OzDES host galaxy spectra requires several processing steps. We first apply a flux calibration by `mangling' the spectrum such that the integrated flux over the wavelength ranges of the DES photometric bands matches that measured in the photometry (further details on the mangling process are provided in \citealt{Swann2020}). Rather than using global galaxy photometry (i.e. using a Kron aperture), we use a circular aperture of diameter 2\arcsec, matching the size of the spectrograph fibres.

>>>>

\section{Estimating host galaxy properties}
\label{sec:measure}
\subsection{Photometric stellar parameters \label{subsec:sedfit}}
To estimate the physical properties of the DES RET host galaxies, we generate synthetic photometry in the DES $griz$ bands by combining the individual SEDs of simple stellar population models. We simulate a suite of synthetic galaxy star-formation histories from which we synthesise model SEDs using stellar population models from \citet{Bruzual2003}  and a \citet{Chabrier2003} initial mass function (IMF).  The suite of models is drawn from the same distribution of parameters as used in \citet{Kauffmann2003} and similar papers \citep[e.g.][]{Gallazzi2005,Gallazzi2009} and closely follows the method of \citet{Childress2013}. From the synthetic SEDs we derive model magnitudes in the DES $griz$ bands and compare them to the observed \replylluis{Kron} magnitudes \replylluis{from the deep photometric catalogue of \citet{Wiseman2020}}. For each set of model and observed magnitudes we calculate a $\chi^2$ value, and from these calculate a PDF for key model parameters (mass-to-light ratio $M/L$, from which we derive $M_*$, and specific star-formation rate sSFR). To estimate uncertainties, we take the values at the 16th and 84th percentiles of the resulting PDF to be our $1\sigma$ lower and upper bounds. The results are presented in Table \ref{tab:derived}. \replylluis{These parameters are estimated using global photometry of the entire galaxies, and thus represent the overall stellar population characteristics.}

\subsection{Spectroscopic gas-phase parameters \label{subsec:linefit}}

To estimate parameters from the OzDES host galaxy spectra requires several processing steps. We first apply a flux calibration by `mangling' the spectrum such that the integrated flux over the wavelength ranges of the DES photometric bands matches that measured in the photometry (further details on the mangling process are provided in \citealt{Swann2020}). We use a circular aperture of diameter 2\arcsec, matching the size of the spectrograph fibres. \replylluis{This way the resulting spectrum is a more accurate representation of the true spectrum at that point in the galaxy. This only holds, however, for the area covered by the fibre and we note that the resulting spectrum is not necessarily representative of the galaxy as a whole. There are several reasons this may not be the case, such as metallicity and age gradients or structure such as bars and discs (see e.g. \citealt{Iglesias-Paramo2013,Iglesias-Paramo2016}), and proceed with our analysis with this caveat acknowledged.}
